---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---

```{r setup, include=FALSE}
library(GeoPack)
```

## Planned Functions for GeoPack

### Load Data

```{r}
democracy_data <- load_data()
head(democracy_data)
```

This loads the full merged dataset from the package's inst/ folder.

### Plot Regime Changes

```{r}
democracy_data = load_data()
plot_regime_changes(democracy_data, top_n = 10, color_by = "continent")
```

This should make a horizontal bar chart of the top N most politically 
unstable countries, colored by continent, showing total regime changes 
from 1950–2022.

---

### Summarise Country Economics

```{r}
masterSet<-load_data()
summarise_country(masterSet, country = "Thailand")
```

This should return a summary table for a given country showing GDP growth, 
unemployment rate, and number of regime changes over time.

---

### Plot GDP vs Unemployment

```{r}
masterSet<-load_data()
plot_gdp_vs_unemployment(masterSet, start_year = 2000, end_year = 2020, democracy_only = FALSE)
```

This should make a scatterplot of unemployment rate vs log GDP, with 
democracies and non-democracies colored differently and optional filtering 
by year range or democracy status.

### Filter Year Range

```{r}
masterSet <- load_data()
filter_year_range(masterSet, start_year = 2000, end_year = 2019)
```

This filters the dataset to a given year range and drops rows with 
missing values in key economic and political columns.

---

### Summarise Continent

```{r}
masterSet <- load_data()
summarise_continent(masterSet, year_range = c(2000, 2020))
```

This returns a summary table by continent showing average GDP growth, 
average unemployment rate, and percentage of country-years classified 
as democratic.

---

### Analyse GDP and Democracy

```{r}
masterSet <- load_data()
analyse_gdp_democracy(masterSet, start_year = 1990, end_year = 2019)
```

This fits a linear regression of log GDP on unemployment rate, democracy 
status, their interaction, and year. Returns a tidy coefficient table 
with 95% confidence intervals. 2020 is excluded due to COVID-19.
