---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Planned Functions for GeoPack

### Plot Regime Changes

```{r}
democracy_data = load_data()
plot_regime_changes(democracy_data, top_n = 10, color_by = "continent")
```

This should make a horizontal bar chart of the top N most politically 
unstable countries, colored by continent, showing total regime changes 
from 1950–2022.

---

### Summarise Country Economics

```{r}
masterSet<-load_data()
summarise_country(masterSet, country = "Thailand")
```

This should return a summary table for a given country showing GDP growth, 
unemployment rate, and number of regime changes over time.

---

### Plot GDP vs Unemployment

```{r}
masterSet<-load_data()
plot_gdp_vs_unemployment(masterSet, start_year = 2000, end_year = 2020, democracy_only = FALSE)
```

This should make a scatterplot of unemployment rate vs log GDP, with 
democracies and non-democracies colored differently and optional filtering 
by year range or democracy status.
